% center for academic English may have good resources
% font should 12pt -> 11pt
\documentclass[a4paper, twoside, 12pt]{report}

% Extra maths symbols (nexists)
\usepackage{amssymb}


\usepackage[dvipsnames]{xcolor}

%% Language and font encodings
\usepackage[english]{babel}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}

%% Sets page size and margins
\usepackage[a4paper,top=3cm,bottom=2cm,left=3cm,right=3cm,marginparwidth=1.75cm]{geometry}

%% Useful packages
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[colorinlistoftodos]{todonotes}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}

% Allow landscape
\usepackage{pdflscape}

% Controls spacing
\usepackage{parskip}

% verbatim with maths (lstlisting)
\usepackage{listings}
\lstset{
  basicstyle=\ttfamily,
  mathescape,
  breaklines=true,
  columns=flexible,
}


% Table column centering
\usepackage{array}
\newcolumntype{P}[1]{>{\centering\arraybackslash}p{#1}}
\newcolumntype{M}[1]{>{\centering\arraybackslash}m{#1}}

% For references
\usepackage[backend=biber]{biblatex}
\addbibresource{bibs/export.bib}

% Example numbering
\usepackage{amsthm}

% Additional maths symbols
\usepackage{mathtools}
\def\multiset#1#2{\ensuremath{\left(\kern-.3em\left(\genfrac{}{}{0pt}{}{#1}{#2}\right)\kern-.3em\right)}}

% Enumerate examples
\theoremstyle{definition} % Use normal font for examples
\newtheorem{example}{Example}


\title{Automatic Concept Extraction and Its Use in Explaining Video Classification}
\author{Roko Parać}
% Update supervisor and other title stuff in title/title.tex

\begin{document}
\renewcommand{\vec}[1]{\textbf{#1}}
\newcommand{\curly}[1]{\mathcal{#1}}
\newcommand{\expct}{\mathbb{E}}
\newcommand{\reals}{\mathbb{R}}


\input{title/title.tex}

% Condensed version of the introduction
% Needs to answer questions: Why? What? How? What are the outcomes?

\begin{abstract}
For most tasks, end-to-end neural networks are undisputedly the best performing and most widely used models in machine learning.
However, they are mostly uninterpretable, making them tricky to apply in a high-risk environment.
Choosing an interpretable model, on the other hand, would yield a decrease in performance.

Recent work on concept bottleneck models \cite{RefWorks:RefID:35-koh2020concept} has managed to design a neural network model which overcomes this issue.
It allows reasoning about a prediction with high-level concepts whilst achieving a competitive accuracy as its end-to-end counterpart.
These concepts, however, need to be manually engineered and labelled to achieve such results.

In this project, we improve the concept bottleneck design by automatically mining concepts from text explanations and improving their interpretability.
To do so, we design a domain-independent concept mining framework using the state-of-the-art approaches from Inductive Logic Programming, Natural Language Processing and Deep Learning.
We showcase that the new framework is a lot better at finding useful concepts than its predecessor, developed by Jeyakumar et al. \cite{RefWorks:RefID:16-2021automatic}, capturing twice as much information about the final labels.\\
In addition, we show that Inductive Logic Programming can be an effective framework for tackling sequence-to-sequence NLP tasks with few available examples, as we achieved Jaccard Index values of 0.55 and 0.85 for two challenging tasks. \\
Finally, to improve the concept bottleneck explainability, we designed a fully interpretable probabilistic logic-based classification framework. It even outperformed the current end-to-end approaches for the MLB-V2E and the sudoku grid validity datasets.

\end{abstract}

\renewcommand{\abstractname}{Acknowledgements}
\begin{abstract}
I would like to express my sincere gratitude to my supervisors Dr. Luke Dickens and Dr. Alessandra Russo, for their academic guidance throughout this process.
They helped me tremendously with their immense knowledge and commitment, and I am grateful to have had them as my supervisors.

My thanks and appreciations also go to my colleagues and friends, who have been a constant source of motivation and have enriched my student life.

Fundamentally, I am beyond grateful to my family. The completion of my studies could not have been possible without their unwavering support, love and encouragement.

\end{abstract}


\tableofcontents
% \listoffigures
% \listoftables

\input{introduction/introduction.tex}
\input{background/background.tex}
\input{solving-nlp-tasks-logically/solving-nlp-tasks-logically.tex}
\input{concept-bottleneck-pipeline/concept-bottleneck-pipeline.tex}
\input{logic-based-classification/logic-based-classification.tex}
\input{related-work/related-work.tex}
\input{conclusion/conclusion.tex}
\input{appendix/appendix.tex}

%\bibliographystyle{alpha}
%\bibliography{bibs/sample}

%\bibliographystyle{plainnat}
%\bibliography{bibs/export.bib}

\printbibliography

\end{document}