\appendix
\chapter{Ethics}

The following section is based on the ethics checklist provided by the Computing Department. 
The checklist consists of a series of yes/no questions. 
If an answer was yes, there is an ethical issue that needs to be considered.
These answers will form a basis for the discussion in this chapter. \\


\emph{"Does the project involve human participants?"}
The project will involve human participants in two ways: 

    - For result validation. Some results obtained in the project have been obtained with human participants, e.g. generated explanation correctness.
    
    - For dataset construction. The datasets used for this project, MLB-V2E \cite{RefWorks:RefID:16-2021automatic} and MSR-V2E \cite{RefWorks:RefID:16-2021automatic}, used human-generated explanations.

Both cases are not harmful to anyone involved. The only care that needs to be taken is regarding the personal information of the subjects involved, which is discussed in the following question.
Additionally, the participants involved in the dataset construction were compensated 15\$ per hour, as discussed in the paper under review \cite{RefWorks:RefID:16-2021automatic}.\\

\emph{"Does your project involve personal data collection and/or processing?"}

The dataset construction required subjects to explain a video in their own words.
But, this data is entirely anonymous and cannot be de-anonymised.
No explanation that is provided is in any way, shape or form personally identifiable information so that it can be linked back to a specific person.

Any data acquired from new participants during this project will be fully anonymised as well. \\

\emph{Will your project use or produce software for which there is a copyrighting licensing implication?}
The project uses three different, third-party pieces of software.
These are \emph{spacy} \cite{RefWorks:RefID:24-spacy}, \emph{FastLAS} \cite{RefWorks:RefID:19-law2020fastlas:}, \emph{ILASP} \cite{RefWorks:RefID:18-law2020ilasp}, and \emph{clingo} \cite{RefWorks:RefID:22-clingo}.
\emph{FastLAS}, \emph{spacy} and \emph{clingo} use the MIT License \cite{RefWorks:RefID:53-mit}.
The MIT License is a permissive license that does not block any future publication and only requires the preservation of copyright and license notices.
On the other hand, \emph{ILASP} is free for use for university research, but it will require reaching out to Mark Law for commercial purposes \cite{RefWorks:RefID:54-ilasp}.
The licenses are not an issue as it stands. \\


To sum up, this project has no outstanding ethical issues which need to be resolved.

\chapter{First Appendix}